---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# taoteprog

This is an analysis package for [Tao Te Programming](http://www.burns-stat.com/documents/books/tao-te-programming/) book. The main goal is to study "alliance graph" of programming advice. `taoteprog` provides the following data:

- `tot_chapters` - a [tibble](http://tibble.tidyverse.org/) with information about chapters. Has two columns: `chapter` (for chapter number) and `name` (for chapter name).
- `tot_edges` - a `tibble` with information about chapter connections (considered as edges in "alliance graph"). Has three columns: `chapter1` and `chapter2` with chapter number of edge vertices and
`type` with "ally" or "opponent" type.

## Installation

You can install taoteprog from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("echasnovski/taoteprog")
```
